---
title: "Replication of 'Democratization and Linguistic Complexity: The Effect of Franchise Extension on Parliamentary Discourse, 1832--1915'"
author: "Grace Jensen"
theme: default
---

```{r}
rm(list=ls())

library(pacman)
pacman::p_load(tidyverse,
               ggplot2,
               effects,
               plm,
               koRpus) 

load("bigframe.rdata")
```

# recalculate FRE scores 
```{r}
# manually recalcualting Fresch score
big.frame <- big.frame %>%
  mutate(FRE_recal = 206.835 -
           1.015 * (word.count/sentence.count) -
           84.6 * (syllable.count/word.count))

```

#Figure 1 is a boxplot and histogram of the data
```{r}
## Fig 1, boxplot and hist

# saving the og version
png("outputs/fig_1_og.png", width = 800, height = 600)

par(bg="white")
par(mfrow=c(1,2))

# making a boxplot and histogram showing distribution of FRE scores across speeches- RESEARCHERS VERSION
boxplot(big.frame$FRE_recal, ylab="FRE", col="cornsilk2")
hist(big.frame$FRE_recal, main="", xlab="", col="cornsilk2")
box()

dev.off()

# MY REMAKES USING GGPLOT
boxplot <- ggplot(big.frame, aes(y = FRE_recal)) + 
       geom_boxplot(fill = "cornsilk2", color = "black") +
  labs(ylab = "FRE") +
  theme_minimal()

histogram <- ggplot(big.frame, aes(x = FRE_recal)) + 
       geom_histogram(fill = "cornsilk2", color = "black") +
  labs(ylab = "FRE") +
  theme_minimal()

ggsave("outputs/fig_1_boxplot.png", boxplot)
ggsave("outputs/fig_1_boxplot.png", histogram)


```

#Table 2 is a summary of the FRE statistics for the sample,
```{r}
##Table 2
print(summary(big.frame$FRE_recal))
print(summary(big.frame$FRE_recal))

##Table 2 (std dev)
print(sd(big.frame$FRE_recal))

# shows that the average FRE score is around 50
```

#Figure 2 is an overtime plot of the cabinet vs noncabinet MPs (means)
```{r}
##Fig 2: overtime plot of cab and non cab

#sessions are the time dummies
sessions <- as.character( unique(big.frame$year.dummy) )

#set up some vectors
wcountcab <- c()
wcountnon <- c()
FKcab <- c()
FKnon <- c()

for(i in 1:length(unique(big.frame$year.dummy))){
  
  sub <- big.frame[big.frame$year.dummy==unique(big.frame$year.dummy)[i],]
  
  subcab <- sub[sub$cabinet==1,]
  wcountcab <- c(wcountcab, mean(subcab$word.count)) #GRACE- ARE THEY DOING ANYTHING WITH THIS VAR? CAN IT BE DELETED?
  FKcab <- c(FKcab, mean(subcab$FK_read.ease))
  
  subnon <- sub[sub$cabinet==0,]
  wcountnon <- c(wcountnon, mean(subnon$word.count))
  FKnon <- c(FKnon, mean(subnon$FK_read.ease))
}

# Create a data frame for plotting
plot_data <- data.frame(
  sessions = rep(sessions, 2),
  FRE_score = c(FKcab, FKnon),
  group = rep(c("Cabinet", "Non-Cabinet"), each = length(sessions))
)

# Manually specify breaks and labels for the x-axis
custom_breaks <- seq(1, length(sessions), length.out = 6)
custom_labels <- sessions[custom_breaks]

#plot mean FRE scores for cab and noncab over time
#png("outputs/fig2_line_plot_og.png", width = 800, height = 600)

par(mfrow=c(1,1))

plot(1:length(sessions), FKcab, axes=F, pch=22, col="black", bg="pink", cex=1.5,
     ylab="FRE", xlab="" )
axis(1, at=1:length(sessions), labels=sessions)
axis(2)
points(1:length(sessions), FKnon, pch=21, col="black", bg="green", cex=1.5)
box()
legend("topleft", pch=c(22,21), col=c("black","black"), pt.bg=c("pink","green"), 
       legend=c("cabinet","non-cabinet"), pt.cex=c(1.5,1.5), bty="n")

low.cab <- lowess(1:length(sessions),FKcab)
lines(low.cab$x, low.cab$y, lwd=4, col="pink")

low.non <- lowess(1:length(sessions), FKnon)
lines(low.non$x, low.non$y, lwd=4, col="green")

#dev.off()

# shows that cabinet member speeches did get less complex over time compared to non-cabinet members
```


```{r}
##Fig 2: overtime plot of cab and non cab

fig2_df <- big.frame %>%
  group_by(cabinet, year.dummy) %>%
  summarize(avg_FRE = mean(FRE_recal))

ggplot(fig2_df, aes(x = year.dummy, y = avg_FRE, color = as.factor(cabinet))) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +
  geom_smooth(method = "loess", se = FALSE, size = 1, aes(group = cabinet)) +
  labs(x = "Session",
       y = "FRE",
       color = "Cabinet") +
  scale_x_discrete(breaks = unique(fig2_df$year.dummy)[seq(1, length(unique(fig2_df$year.dummy)), length.out = 6)]) +
  theme_minimal() +
  scale_color_manual(values = c("green", "pink"), labels = c("non-cabinet", "cabinet"))+
  scale_shape_manual(values = c(22)) +
  theme(legend.position = c(0.13, 0.85)) +
  guides(color = guide_legend(override.aes = list(fill = c("green","pink")),
                              title = "Legend",
                              keywidth = 1.5,
                              keyheight = 1.5))
  

# shows that cabinet member speeches did get less complex over time compared to non-cabinet members
```

#Figure 3 plots sentence length and syllables per word (mean overview) for cabinet and non-cabinet
```{r}
#sessions <- as.character( unique(big.frame$year.dummy) )
#ALREADY SET UP THSI VAR SO NOT NECESSARY

#matrix to take the results
res.mat <- data.frame(cab.sent=NA, cab.syll=NA, non.sent=NA, non.syll=NA)

for(i in 1:length(sessions)){
  dat <- big.frame[big.frame$year.dummy==sessions[i], ]
  
  
  cab <- dat[dat$cabinet==1,]
  cab.sent.length <- mean(cab$word.count/cab$sentence.count)
  res.mat[i,1] <- cab.sent.length
  
  cab.syll <- mean(cab$syllable.count/cab$word.count)
  res.mat[i,2] <- cab.syll
  
  noncab <- dat[dat$cabinet==0,]
  non.sent.length <- mean(noncab$word.count/noncab$sentence.count)
  res.mat[i,3] <- non.sent.length
  
  non.syll <- mean(noncab$syllable.count/noncab$word.count)
  res.mat[i,4] <- non.syll
  
}

#png("outputs/fig3_line_plot.png", width = 1000, height = 600)

par(mfrow=c(1,2))
par(mgp= c(2, 1, 0))

#plot words per sentence
plot(1:length(sessions),res.mat[,1], ylab="mean sent length", xlab="", type="l", lwd=2, axes=F)
lines(1:length(sessions), res.mat[,3], lwd=1, lty=2)
axis(1,at=1:length(sessions), sessions)
axis(2)
box()
legend("bottomleft",lty=c(1,2), lwd=c(2,1), col=c("black","black"), legend=c("cab","noncab"), bty="n")

#plot syllables per word
plot(1:length(sessions), res.mat[,2], ylab="mean sylls per word", xlab="", type="l", lwd=2, axes=F)
lines(1:length(sessions), res.mat[,4], lwd=1, lty=2)
axis(1,at=1:length(sessions), sessions)
axis(2)
box()
legend("bottomleft",lty=c(1,2), lwd=c(2,1), col=c("black","black"), legend=c("cab","noncab"), bty="n")

#dev.off()
```
```{r}
# GGPLOT VERSION 
#GRACE VERSION
for(i in 1:length(sessions)){
  
  sub <- big.frame[big.frame$year.dummy==unique(big.frame$year.dummy)[i],]
  
  subcab <- sub[sub$cabinet==1,]
  FKcab <- c(FKcab, mean(subcab$FRE_recal))
  
  subnon <- sub[sub$cabinet==0,]
  wcountnon <- c(wcountnon, mean(subnon$word.count))
  FKnon <- c(FKnon, mean(subnon$FRE_recal))
}
```

#Figure 4 plots average length of speeches for cabinet and noncabinet MPs over time
```{r}

#set up some vectors to take results
wcountcab <- c()
wcountnon <- c()


for(i in 1:length(unique(big.frame$year.dummy))){
  
  sub <- big.frame[big.frame$year.dummy==unique(big.frame$year.dummy)[i],]
  
  subcab <- sub[sub$cabinet==1,]
  wcountcab <- c(wcountcab, mean(subcab$word.count))
  
  subnon <- sub[sub$cabinet==0,]
  wcountnon <- c(wcountnon, mean(subnon$word.count))
  
}

png("outputs/fig4_line_plot.png", width = 1000, height = 600)

plot(1:length(sessions), wcountcab, axes=F, pch=22, col="black", bg="pink", cex=1.5,
     ylab="", xlab="" )
axis(1, at=1:length(sessions), labels=sessions)
axis(2)
points(1:length(sessions), wcountnon, pch=21, col="black", bg="green", cex=1.5)
box()
legend("topleft", pch=c(22,21), col=c("black","black"), pt.bg=c("pink","green"), 
       legend=c("cabinet","non-cabinet"), pt.cex=c(1.5,1.5))

dev.off

```

#Figure 5 is boxplot comparing Hardie and Balfour (texts as given in appx)
```{r}

png("outputs/fig5_line_plot.png", width = 800, height = 600)

balfour <-c(47.72460, 51.63518, 43.67178, 52.70469, 50.90355,44.95354, 45.09750)

hardie <-c(64.4283469809544, 63.9055768205566, 50.5082182657076, 61.3105436303335, 55.1278390113993, 58.8502434353679, 63.5047437731243, 60.3454720293998)

boxplot(balfour, hardie, names=c("Balfour","Hardie"), ylab="score")
```

#Figure 6 is estd bhat on the session-by-session regressions
```{r}
sessions <- as.character( unique(big.frame$year.dummy) )

#matrix to store results
coef.frame <- data.frame(sess=unique(big.frame$year.dummy), est = as.numeric(NA), se = as.numeric(NA), lo=as.numeric(NA), hi=as.numeric(NA), pval=as.numeric(NA))

#clus SEs function (courtesy of Drew Dimmery)
cl   <- function(dat,fm, cluster){
  require(sandwich, quietly = TRUE)
  require(lmtest, quietly = TRUE)
  M <- length(unique(cluster))
  N <- length(cluster)
  K <- fm$rank
  dfc <- (M/(M-1))*((N-1)/(N-K))
  uj  <- apply(estfun(fm),2, function(x) tapply(x, cluster, sum));
  vcovCL <- dfc*sandwich(fm, meat=crossprod(uj)/N)
  coeftest(fm, vcovCL) }

for(i in 1:length(sessions)){
  
  dat <- big.frame[big.frame$year.dummy==sessions[i],]
  dat <- dat[complete.cases(dat),]
  
  #main regression
  mod <- lm(FRE_recal ~ party + cabinet+ word.count + competitiveness, data= dat)
  
  #fix SEs
  # apply the 'cl' function , cluster on mp
  mod.clus.SE <-cl(dat, mod, dat$mp_code)
  
  
  coefs <- mod.clus.SE
  coef.frame[i,c(2,3)] <- as.numeric(coefs["cabinet1",c(1,2)])
  
  coef.frame[i,4] <- coefs["cabinet1",c(1)] + ( 1.96*as.numeric(coefs["cabinet1",2]))
  coef.frame[i,5] <- coefs["cabinet1",c(1)] -( 1.96*as.numeric(coefs["cabinet1",2]))
  coef.frame[i,6] <- coefs["cabinet1",4]
  
  cat("\n done",sessions[i],"\n")
  
}

ylimup <-  max(c(coef.frame$lo, coef.frame$hi))
ylimdown <- min(c(coef.frame$lo, coef.frame$hi))

png("outputs/fig6_line_plot.png", width = 1000, height = 600)

plot(1:nrow(coef.frame), coef.frame$est, type="p", pch=16, ylim=c(ylimdown, ylimup), axes=F, xlab="",
     ylab="")

mtext(expression(hat(beta)), side=2, line=2, cex=1.5, srt=90 )

par(las=1)
axis(2)
axis(1, at=1:nrow(coef.frame), labels=coef.frame$sess, cex.axis=.7, las=1)
box()

arrows(1:nrow(coef.frame), coef.frame$lo, 1:nrow(coef.frame), coef.frame$hi, code=3, angle=90, length=.05)
abline(h=0, col="red", lwd=2)  

#do structural break test
require(strucchange)
y <- coef.frame$est
x <- 1:nrow(coef.frame)
print(breakpoints(y~x)) 

dev.off()
```

#Table 4 is the 'main' set of regression results contains two models: one with several variables, second wiht just the interaction
```{r}
#make the 1868_1 dummy
reform.act <- rep(0, times=length(big.frame$year.dummy))
m <- match("1868_1", big.frame$year.dummy)
reform.act[m:length(big.frame$year.dummy)] <- 1
big.frame$reform.act <- reform.act

#do an lm with only the interaction
mod.int <- lm(FRE_recal ~   cabinet*reform.act, data= big.frame)

#do an lm with the controls, too
mod <- lm(FRE_recal ~ party + cabinet +word.count +competitiveness + cabinet*reform.act, data= big.frame)

#clustered SEs (via Drew Dimmery's code)
cl   <- function(dat,fm, cluster){
  require(sandwich, quietly = TRUE)
  require(lmtest, quietly = TRUE)
  M <- length(unique(cluster))
  N <- length(cluster)
  K <- fm$rank
  dfc <- (M/(M-1))*((N-1)/(N-K))
  uj  <- apply(estfun(fm),2, function(x) tapply(x, cluster, sum));
  vcovCL <- dfc*sandwich(fm, meat=crossprod(uj)/N)
  coeftest(fm, vcovCL) }

# apply the 'cl' function , cluster on mp
cat("---------------------------------\n")
cat("Simple model: interaction only\n")
mod.clus.reform.int <- cl(big.frame, mod.int, big.frame$mp_code)
print(mod.clus.reform.int)
cat("\n R^2=",summary(mod.int)$r.squared,"\n")
cat("\n adj R^2=",summary(mod.int)$adj.r.squared,"\n")


cat("---------------------------------\n")
cat("Model with controls\n")
mod.clus.reform <-cl(big.frame, mod, big.frame$mp_code)
print(mod.clus.reform)
cat("\n R^2=",summary(mod)$r.squared,"\n")
cat("\n adj R^2=",summary(mod)$adj.r.squared,"\n")
```

#Figure 7 is the estimated marginal effect of the reform act interaction.

```{r}
robust.se <- function(model, cluster){
  require(sandwich)
  require(lmtest)
  M <- length(unique(cluster))
  N <- length(cluster)
  K <- model$rank
  dfc <- (M/(M - 1)) * ((N - 1)/(N - K))
  uj <- apply(estfun(model), 2, function(x) tapply(x, cluster, sum));
  rcse.cov <- dfc * sandwich(model, meat = crossprod(uj)/N)
  rcse.se <- coeftest(model, rcse.cov)
  return(list(rcse.cov, rcse.se))
}

clustervar<-mapply(paste,"MP.",big.frame$mp_code, sep="")
mod2int <- mod.int
mod2int$coeftest <- robust.se(mod.int,clustervar)[[2]]
mod2int$se <- robust.se(mod.int,clustervar)[[2]][,2]

#make robust SEs
vcov.cluster <- robust.se(mod.int,clustervar)[[1]]

#use Anton strezhnev's code for interaction plot (modulo some clean up on plotting
# and handling of SEs.)

interaction_plot_binary <- function(model, effect, moderator, interaction, varcov="default", conf=.95, title="Marginal effects plot", xlabel="Value of moderator", ylabel="Estimated marginal coefficient", factor_labels=c(0,1)){
  
  # Extract Variance Covariance matrix
  ifelse(varcov == "default", covMat <- vcov(model), covMat <- varcov)
  
  # Extract the data frame of the model
  mod_frame = model.frame(model)
  
  # Get coefficients of variables
  beta_1 = model$coefficients[[effect]]
  beta_3 = model$coefficients[[interaction]]
  
  # Create list of moderator values at which marginal effect is evaluated
  x_2 <- c(0,1)
  
  # Compute marginal effects
  delta_1 = beta_1 + beta_3*x_2
  
  # Compute variances
  var_1 = covMat[effect,effect] + (x_2^2)*covMat[interaction, interaction] + 2*x_2*covMat[effect, interaction]
  
  # Standard errors
  se_1 = sqrt(var_1)
  
  # Upper and lower confidence bounds
  z_score = qnorm(1 - ((1 - conf)/2))
  upper_bound = delta_1 + z_score*se_1
  lower_bound = delta_1 - z_score*se_1
  
  # Determine the bounds of the graphing area
  max_y = max(upper_bound)
  min_y = min(lower_bound)
  
  # Initialize plotting window
  plot(x=c(), y=c(), ylim=c(min_y, max_y), xlim=c(-.5, 1.5), xlab=xlabel, ylab=ylabel, main=title, xaxt="n")
  
  # Plot lines of confidence intervals
  #when moderator==0
  arrows(x_2[1],lower_bound[1], x_2[1],upper_bound[1], code=3, angle=90, lwd=2)
  
  #when moderator == 1
  arrows(x_2[2],lower_bound[2], x_2[2],upper_bound[2], code=3, angle=90, lwd=2)
  
  # Plot points of estimated effects
  points(x=x_2, y=delta_1, pch=21, col="black", bg="blue", cex=2)
  
  # Label the axis
  axis(side=1, at=c(0,1), labels=factor_labels)
  
  # Add a dashed horizontal line for zero
  abline(h=0, lty=3)
  
}

png("outputs/fig7_plot.png", width = 1000, height = 600)
par(mfrow=c(1,1))


#do the plot
interaction_plot_binary(mod.int, effect="cabinet1" , moderator="reform.act" , 
                        interaction="cabinet1:reform.act", varcov=vcov.cluster,
                        title="", xlabel="Reform Act", ylabel="Est marginal coef on Cabinet",
                        factor_labels=c("before","after"))
dev.off()
```

#Figure 8: look at cabinet members in  models with and without fixed effects if estimates overlap, have evidence that individual latent types are not very important

```{r}
require(plm)

#only look at cabinet members
big.frame<- big.frame[big.frame$cabinet==1,]
#get rid of NAs
big.frame <- big.frame[complete.cases(big.frame),] 

#make into panel data
#-> requires aggregates to means/medians per year
# regress y ~ parl time dummies
# regress y ~ parl time dummies + mp fixed effects
# IF parl time dummies are very different in second spec then 
# mp fixed effects "matter"

#first, make into yearly data
require(plyr)
yeardata  <- ddply(big.frame, .(year.dummy, mp_code), summarize, y = mean(FRE_recal))

mod.year <- lm(y~ year.dummy , data=yeardata) #don't fit to x

#now allow fixed effects
require(plm)
#don't have to fit cabinet regressor
mod.fe <- plm(y ~  year.dummy  , data = yeardata, index = c("mp_code","year.dummy"), 
              model = "within")

#store reg output
summ.year <- summary(mod.year)
summ.year_coef <-summary(mod.year)$coef
summ.fe <- summary(mod.fe)
summ.fe_coef <- summary(mod.fe)$coef


#function to take estimate row and produce lower and upper bound (95%)
make.95<-function(x=summ.year_coef[2,]){
  low <- x[1] - (1.96*x[2]) 
  hi <- x[1] + (1.96*x[2])
  out <- as.vector(c(low,hi))
  out
}


#now we want to see if the year dummies overlap (95% CIs)
compare.frame <- data.frame(nofe.est= NA, nofe.low=NA, nofe.hi=NA, fe.est=NA , fe.low =NA , fe.hi=NA)

for(i in 1:length(row.names(summ.fe_coef))){
  
  name.no.fe <- row.names(summ.fe_coef)[i]
  compare.frame[i,1] <- summ.year_coef[name.no.fe,1] #just grab the pt estimates for the constant
  compare.frame[i,c(2,3)] <- make.95(summ.year_coef[name.no.fe,])
  
  
  compare.frame[i,4] <- summ.fe_coef[name.no.fe,1] #grab pt estimate for each one
  compare.frame[i,c(5,6)] <- make.95(summ.fe_coef[name.no.fe,])
  
  
  
}

#label rows
row.names(compare.frame) <- row.names(summ.fe_coef)


par(bg='cornsilk1')
plot(1:nrow(compare.frame), seq(min(compare.frame), max(compare.frame), length=nrow(compare.frame)), 
     type="n",xlab="session", ylab="estimate", axes=F )

axis(1, at= 1:nrow(compare.frame),labels=gsub("year.dummy","",row.names(compare.frame)))
axis(2)
box()

legend("bottomright",pch=c(16,16), lty=c(1,3), col=c("black", "red"), legend=c("w/o fixed effs","fixed effs"))

for(j in 1:nrow(compare.frame)){
  
  points(j, compare.frame[j,1], pch=16,col="black")  
  arrows(j, compare.frame[j,2], j , compare.frame[j,3], code=3, length=0)  
  
  
  points(j+.3, compare.frame[j+.3,4],pch=16, col="red")
  arrows(j+.3, compare.frame[j+.3,5], j+.3 , compare.frame[j+.3,6], code=3, length=0, col="red", lty=3, lwd=1.5)  
  
  
}
```

#Figure 9: proportion of all speeches are made by cabinet vs non cabinet

```{r}
sessions <- unique(big.frame$year.dummy)
speeches.cab <- c()
speeches.non <- c()
tot.speeches <- c()
mean.len.cab <- c()
mean.len.non <- c()


for(i in 1:length(sessions)){
  dat <- big.frame[big.frame$year.dummy==sessions[i],]
  tot.speeches <- c(tot.speeches, nrow(dat))
  speeches.cab <- c(speeches.cab,nrow(dat[dat$cabinet==1,]))
  speeches.non <- c(speeches.non,nrow(dat[dat$cabinet==0,]))
  
  mean.len.cab <- c(mean.len.cab, mean(dat$word.count[dat$cabinet==1]))
  mean.len.non <- c(mean.len.non, mean(dat$word.count[dat$cabinet==0]))
}

par(bg='cornsilk1')
par(mfrow=c(1,1))
plot(speeches.cab/tot.speeches,lwd=2, ylim=c(0,1), type="l", axes=F, xlab="", ylab="")
axis(1, at=1:length(sessions), labels=sessions)
axis(2)
lines(speeches.non/tot.speeches, lty=2)
legend("topright", lty=c(1,2), lwd=c(2,1), legend=c("cabinet","non"))
box()
```

#Figure 10: probability a minister speaks following a non-minister for 'middle period' around claimed break

```{r}
require(effects)

#function to regressions and plots
#(egregious use of <<- ... avert thine eyes)
make.pred <- function(sess="1865_1", pre = 0){
  big <<- big.frame[big.frame$year.dummy==sess,]
  curr <<- as.numeric( big$cabinet[-c(1)]) 
  prev <<- as.numeric( big$cabinet[-c(length(big$cabinet))] )
  mod <<- glm(curr ~ prev, family='binomial')
  out <<- as.data.frame(effect("prev", mod))[pre+1,]
  out
}

#do first one of each
preds0 <- make.pred(sess= "1852_1", pre=0) # this is Pr(cab now|bb)
preds1 <-  make.pred("1859_1", pre=1) # this is Pr(cab now|cab)


sessions <- c( "1852_2",  "1852_3",  "1852_4" , "1852_5" ,  "1857_2" , "1857_3"  , "1859_1","1859_2", "1859_3", "1859_4", "1859_5", "1859_6", 
               "1859_7", "1865_1", "1865_2", "1865_3", "1868_1", "1868_2", "1868_3", 
               "1868_4", "1868_5", "1874_1", "1874_2", "1874_3", "1874_4", "1874_5", 
               "1874_6", "1874_7")

for(i in 1: length(sessions)){
  preds0 <- rbind(preds0, make.pred(sessions[i], pre=0)) #ERROR EITH PREDS0
  preds1 <- rbind(preds1, make.pred(sessions[i], pre=1))
  
  
}

par(bg='cornsilk1')
plot(1:nrow(preds0), preds0$fit, ylim=c(min(preds0$lower),max(preds0$upper)), axes=F, 
     xlab="",ylab="", pch=16)
par(las=2)
axis(1,at=1:nrow(preds0), labels= c("1852_1",sessions))
axis(2)
for(i in 1:nrow(preds0)){
  arrows(i, preds0[i,4], i, preds0[i,5],code=3, angle=90, length=.05 )
}
box()
```

# Implementing other complexity Measures

```{r}
# copy and paste speeches

samples <- c(
  "Asked the Under Secretary of State for the Colonies whether Her Majesty’s Government have arrived at any practical decision with regard to the establishment of emigration bureaux for the purpose of promoting as promised early in the Session a systematic system of State-directed emigration?",
  
  "Can the right Honorable Gentleman give the House any information as to when the Royal Commission on the Depression of Trade is likely to report on this subject",
  
  "That i cannot say til i have seen it."
)

# Create a corpus
sample_corpus <- corpus(samples)

all_readability_measures <- textstat_readability(sample_corpus, 
                                                 c("Flesch", "Dale.Chall", 
                                                   "SMOG", "Coleman.Liau"))

tokens <- tokens(sample_corpus, remove_punct = TRUE)
readability_measures <- textstat_readability(sample_corpus, measure = "Dale.Chall")


print(all_readability_measures)
```


